Mixed-Effects Model for MTLD by Gender

### 2018-08-22 paper.Rmd

The ability to easily browse and explore the CHILDES corpora is a cornerstone of the `childes-db` project.
To this end we have created powerful yet easy-to-use interactive web applications that enable users to visualize various dimensions of the CHILDES corpus: frequency counts, mean lengths of utterance, type-token ratios, and more.
All of this is doable without the requirement of understanding command-line tools or any kind of programming knowledge as had been the case with CLAN.^[The LuCiD toolkit [@chang2017] provides related functionality for a number of common analyses.
In contrast to those tools, which focus on filling gaps not covered by CLAN -- e.g., the use of $n$-gram models, incremental sentence generation, and distributional word classification -- our web apps focus on covering the same common tasks as CLAN, but making the outputs into browsable visualizations.]

@@

For this analysis, we will define our words of interest as the basic color words of English (except for gray, which children hear very rarely).
We store these in the `colors` variable, and then use the `get_types()` function from `childesr` to get the type frequency of each of these words in all of the corpora in CHILDES.
For demonstration, we look only at the types produced by the speakers in each corpus tagged as Mother and Father.
We also restrict ourselves to children from 1--5 years old (12--60 months), and look only at the North American English corpora.

>>>>

The ability to easily browse and explore the CHILDES corpora is a cornerstone of the `childes-db` project.
To this end we have created powerful yet easy-to-use interactive web applications that enable users to visualize various dimensions of the CHILDES corpus: frequency counts, mean lengths of utterance, type-token ratios, and more.
All of this is doable without the requirement of understanding command-line tools.^[The LuCiD toolkit [@chang2017] provides related functionality for a number of common analyses.
In contrast to those tools, which focus on filling gaps not covered by CLAN -- e.g., the use of $n$-gram models, incremental sentence generation, and distributional word classification -- our web apps focus on covering the same common tasks as CLAN, but making the outputs into browsable visualizations.]

@@

For this analysis, we will define our words of interest as the basic color words of English (except for gray, which children hear very rarely).
We store these in the `colors` variable, and then use the `get_types` function from `childesr` to get the type frequency of each of these words in all of the corpora in CHILDES.
All other functions are provided by base R or the `tidyverse` package. 
For demonstration, we look only at the types produced by the speakers in each corpus tagged as Mother and Father.
We also restrict ourselves to children from 1--5 years old (12--60 months), and look only at the North American English corpora.
